Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-29 paper.tex
up

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. Many scholars have looked into QoS optimisation problems in QoS-aware web service composition, applying AI planning and Evolutionary Computation techniques. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of requirements. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task related services that is decoded into composition solutions. We compare proposed comprehensive quality model with one promising QoS model, and also compare the effectiveness of PSO-based method with one recent GP-based method using comprehensive quality model.

@@

The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality based on our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work as follows:

@@

\section{Experiment Study}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach. To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. $(2)$ measure the effectiveness of our proposed comprehensive quality model. To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our proposed PSO-based approach.

An augmented version of Web service challenge 2009 (WSC09) used in \cite{ma2015hybrid,da2016genetic} including QoS attributes is used for our experiment. WSC09 is a benchmark dataset consisting of five composition tasks that associated with an increasing number of services, and concepts in ontologies.

The parameters are chosen based on the settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125. The returned value of $type(a,b)$ is set to 1 ($Exact$) and 0.75 ($Plugin$) according to \cite{lecue2009optimizing}. In general, weight settings and parameter match type quality are decided by users' preferences.

@@

The first column of Table \ref{meanFitness} shows five tasks from WSC09 Dataset. The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and shrunk service repository size after the greedy search respectively regarding the five tasks. This greedy search helps reducing the repository size by considering only task-related service candidates, which also contributes to a significant reduced researching space. The fourth and fifth column of Table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods. We employ independent-samples T tests to test the significant differences in mean fitness value. The results show that the PSO-based approach outperformes the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01). In task 5, PSO-based approach performs significantly better than GP-based approach in finding optimal solutions. It may refer to that GP-based approach is stuck in the local optimal due to a very large searching space of our composition problem, but PSO-based approach requres a decoding process, and small changes in a sorted queue might lead to a varying decoded solutions. Therefore, PSO-based approach is considered to be hard to be stuck in the local optimal for our composition problem.

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{l|l|l|l|l}
\hline
\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunken $SR$   &PSO-based approach & GP-based approach  \\ \hline
Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
Task 2                     &4129           &140   &0.4701 $\pm$ 0.0011  $\uparrow$  &0.4597 $\pm$ 0.0029          \\ \hline
Task 3                     &8138           &153   &0.5504 $\pm$ 0.0128              &0.5679 $\pm$ 0.0234 $\uparrow$   \\ \hline
Task 4                     &8301           &330   &0.4690 $\pm$ 0.0017  $\uparrow$  &0.4317 $\pm$ 0.0097            \\ \hline
Task 5                     &15211          &237   &0.4694 $\pm$ 0.0008  $\uparrow$  &0.2452 $\pm$ 0.0369            \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[]
\footnotesize
\centering
\caption{Mean values of $SM$ and $QoS$ for QoS evaluation model and comprehensive quality evaluation model using PSO-based approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive Quality \\ Model} \\ \hline
\multirow{2}{*}{Task1}  &$SM$   &0.5373 $\pm$ 0.0267               &0.5580 $\pm$ 0.0094 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164                          \\ \hline
\multirow{2}{*}{Task2}  &$SM$   &0.4549 $\pm$ 0.0033               &0.4630 $\pm$ 0.0042 $\uparrow$ \\ \cline{2-4} 
                        &$QoS$  &0.4800 $\pm$ 0.0012 $\uparrow$    &0.4772 $\pm$ 0.0025 \\ \hline
\multirow{2}{*}{Task3}  &$SM$   &0.5538 $\pm$ 0.0082               &0.6093 $\pm$ 0.0054 $\uparrow$   \\ \cline{2-4} 
                        &$QoS$  &0.4940 $\pm$ 0.0013 $\uparrow$    &0.4913 $\pm$ 0.0009            \\ \hline
\multirow{3}{*}{Task4}  &$SM$   &0.4398 $\pm$ 0.0037               &0.4604 $\pm$ 0.0000 $\uparrow$ \\ \cline{2-4} 
                        &$QoS$  &0.4845 $\pm$ 0.0010 $\uparrow$    &0.4734 $\pm$ 0.0044  \\ \hline
\multirow{3}{*}{Task5}  &$SM$   &0.4580 $\pm$ 0.0065               &0.4639 $\pm$ 0.0013 $\uparrow$           \\ \cline{2-4} 
                        &$QoS$  &0.4764 $\pm$ 0.0005 $\uparrow$    &0.4750 $\pm$ 0.0007  \\ \hline                                                   
\end{tabular}
\end{table}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of requirements. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task-related services that is decoded into composition solutions. We compare the effectiveness of PSO-based method with one recent GP-based method using the proposed comprehensive quality model, and also compare the effectiveness of our proposed comprehensive quality model with one promising QoS model.

@@

The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality based on our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work:

@@

\section{Experiment Study}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach. To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. $(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desired balance of semantic matchmaking quality and QoS. To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.

An augmented version of Web service challenge 2009 (WSC09) used in \cite{ma2015hybrid,da2016genetic} including QoS attributes is used for our experiment. WSC09 is a benchmark dataset consisting of five composition tasks. These tasks are associated with an increasing number of services, and concepts in ontologies.

The parameters are chosen based on the settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure the weights of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125. The returned value of $type(a,b)$ is set to 1 ($Exact$) and 0.75 ($Plugin$) according to \cite{lecue2009optimizing}. In general, weight settings and parameter match type quality are decided by users' preferences.

@@

The first column of Table \ref{meanFitness} shows five tasks from WSC09 Dataset. The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and shrunk service repository size after the greedy search respectively regarding the five tasks. This greedy search helps reducing the repository size by considering only task-related service candidates, which also contributes to a significant reduced researching space. The fourth and fifth column of Table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods. We employ independent-samples T tests to test the significant differences in mean fitness value. The results show that the PSO-based approach outperformes the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01). In task 5, PSO-based approach performs significantly better than GP-based approach in finding optimal solutions. It may refer to that GP-based approach is stuck in the local optimal due to a very large searching space in Task 5, but PSO-based approach requres decoding processes of sorted queues, where small changes of the queues might lead to different decoded solutions.

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{c|c|c|l|l}
\hline
\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunken $SR$   &PSO-based approach & GP-based approach  \\ \hline
Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
Task 2                     &4129           &140   &0.4701 $\pm$ 0.0011  $\uparrow$  &0.4597 $\pm$ 0.0029          \\ \hline
Task 3                     &8138           &153   &0.5504 $\pm$ 0.0128              &0.5679 $\pm$ 0.0234 $\uparrow$   \\ \hline
Task 4                     &8301           &330   &0.4690 $\pm$ 0.0017  $\uparrow$  &0.4317 $\pm$ 0.0097            \\ \hline
Task 5                     &15211          &237   &0.4694 $\pm$ 0.0008  $\uparrow$  &0.2452 $\pm$ 0.0369            \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[]
\footnotesize
\centering
\caption{Mean values of $SM$ and $QoS$ for QoS evaluation model and comprehensive quality evaluation model using PSO-based approach}
\label{decisionTable}
\begin{tabular}{c|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS \\ Evaluation Model}         &\shortstack{Comprehensive Quality \\ Evaluation Model} \\ \hline
\multirow{2}{*}{Task1}  &$SM$   &0.5373 $\pm$ 0.0267               &0.5580 $\pm$ 0.0094 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.5574 $\pm$ 0.0156               &0.5604 $\pm$ 0.0164                          \\ \hline
\multirow{2}{*}{Task2}  &$SM$   &0.4549 $\pm$ 0.0033               &0.4630 $\pm$ 0.0042 $\uparrow$ \\ \cline{2-4} 
                        &$QoS$  &0.4800 $\pm$ 0.0012 $\uparrow$    &0.4772 $\pm$ 0.0025 \\ \hline
\multirow{2}{*}{Task3}  &$SM$   &0.5538 $\pm$ 0.0082               &0.6093 $\pm$ 0.0054 $\uparrow$   \\ \cline{2-4} 
                        &$QoS$  &0.4940 $\pm$ 0.0013 $\uparrow$    &0.4913 $\pm$ 0.0009            \\ \hline
\multirow{3}{*}{Task4}  &$SM$   &0.4398 $\pm$ 0.0037               &0.4604 $\pm$ 0.0000 $\uparrow$ \\ \cline{2-4} 
                        &$QoS$  &0.4845 $\pm$ 0.0010 $\uparrow$    &0.4734 $\pm$ 0.0044  \\ \hline
\multirow{3}{*}{Task5}  &$SM$   &0.4580 $\pm$ 0.0065               &0.4639 $\pm$ 0.0013 $\uparrow$           \\ \cline{2-4} 
                        &$QoS$  &0.4764 $\pm$ 0.0005 $\uparrow$    &0.4750 $\pm$ 0.0007  \\ \hline                                                   
\end{tabular}
\end{table}
